Manuscript

### 2022-07-19 Manuscript.Rmd
big stage to save everything after resetting commit history

For the main analysis, presented here, we sampled $n = 1000$ body sizes from distributions described by five different $\lambda$'s: (-1.5, -1.75, -2.00, -2.25, -2.5). The supplemental information contains results when the value of n is varied (or maybe include in main?). Each value of $\lambda$ was assumed to come from a community across a hypothetical environmental gradient $X$. Values of $X$ for each community are uniformly distributed from -1 to 1. We repeated the data simulation 1000 times (reps). The main results presented here were not dependent on the range of *x*-values or the number of sites (supplemental information).

>>>>

For the main analysis, presented here, we sampled $n = 1000$ body sizes from distributions described by five different $\lambda$'s: (-1.5, -1.75, -2.00, -2.25, -2.5), such that our model for $\lambda$ is:

$$\lambda = Norm(\alpha -0.5X, \sigma)$$

The supplemental information contains results when the value of n is varied (or maybe include in main?). Each value of $\lambda$ was assumed to come from a community across a hypothetical environmental gradient $X$. Values of $X$ for each community are uniformly distributed from -1 to 1. We repeated the data simulation 1000 times (reps). The main results presented here were not dependent on the range of *x*-values or the number of sites (supplemental information).
